LAGOS lake depth

### 2021-08-04 figures/01_geometry.Rmd
turn back on slope compare chunk for data processing purposes

slope_dist_str <- "online_mean|slope_pnt|inlake_slope|dist_v|dist_d|dists_|slope_mean"
# jsta::jheatmap
jheatmap(
  dplyr::select(dt,
    matches(slope_dist_str))
  # maxdepth,
  # meandepth)
)

@@

```{r buffer-vs-inlake_slope, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4}
lgus_pred <- read.csv("../data/lagosus_depth_predictors.csv", stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  dplyr::select(-matches("inlake_slope"),
    -matches("dist_|dists_"))
test <- left_join(dt, lgus_pred, by = c("llid" = "lagoslakeid")) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::arrange(desc(factor(shape_class,
    levels = c("neither", "concave", "convex"))))

>>>>

slope_dist_str <- "online_mean|slope_pnt|inlake_slope|dist_v|dist_d|dists_|slope_mean"
# jsta::jheatmap
# jheatmap(
#   dplyr::select(dt,
#     matches(slope_dist_str))
#   # maxdepth,
#   # meandepth)
# )

@@

```{r buffer-vs-inlake_slope, echo=FALSE, message=FALSE, eval=TRUE, warning=FALSE, results='hide', fig.width=4}
lgus_pred <- read.csv(
  "../data/lagosus_depth_predictors.csv",
  stringsAsFactors = FALSE) %>%
  mutate(lagoslakeid = as.character(lagoslakeid)) %>%
  dplyr::select(
    -matches("inlake_slope"),
    -matches("dist_|dists_")
  )
test <- left_join(dt, lgus_pred, by = c("llid" = "lagoslakeid")) %>%
  dplyr::filter(!is.na(shape_class)) %>%
  dplyr::filter(inlake_slope_pnt < 4) %>%
  dplyr::arrange(desc(factor(shape_class,
    levels = c("neither", "concave", "convex"))))
